---
title: "week 16 tidytuesday"
output:
  html_document:
    df_print: paged
---




```{r data import}
gdpr_violations <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-21/gdpr_violations.tsv')
gdpr_text <- readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-21/gdpr_text.tsv')

```


```{r Loading libraries}
library(tidyverse)
library(lubridate)
library(scales)
```


## Dat transformation 

```{r}
gdpr_violations$date <- as.POSIXct.Date(gdpr_violations$date)

 violation_data <- gdpr_violations  %>% 
  mutate(month = lubridate::month(gdpr_violations$date)) %>% 
  group_by(name)  %>% summarise( total_price = sum(price), count = n()) %>% 
  as.data.frame() %>% select(name, total_price, count)

 head(violation_data)
```


## Exploring relationship between Total fine price and the cases of violation per country

Is it safe to assume that the higher the  total number of violation cases in a country the hefty the fine price?
its interesting to note that countries such as France, Italy and Austria were among the countries that recorded the least number of cases
but then their fine price ranked top most, as such, the higher the total number of violation cases does not necessarily mean a resulting high fine price and vice versa.

Is there some correlation between the total number of violation cases in a country and the total fine price?


```{r}
violation_data %>% ggplot(aes(y = count, x = reorder(name, count), fill = total_price)) + 
  geom_col() + 
  xlab("Country") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggtitle("Total number of cases and fine price per country") +
  coord_flip() + 
    scale_fill_gradient( low = c("#87CEFA"), high = c("#000080"), name = "Total fine price", labels =  dollar_format(suffix = "€", prefix = ""))+
  ylab("Number of cases") +
  geom_text(aes(label = paste0(total_price,"€")), hjust = 0.001) +
  scale_y_continuous(limits = c(0,80),breaks = c(0,20,40,60,80))
 

```


```{r}
ggsave("violation_plot.png")
```

