---
title: "Tidytuesday week 50"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---

# Women of 2020
Data for this week's tidytuesday challenge comes from BBC. It has a list of 100 inspiring and influential women from around the world for 2020.
These are women who are leading change and making a difference during these turbulent times.

I'd like to do some visualization to try and make some deductions from the data as I flex my data visualization skills in this tidytuesday challenge.

## Data import
```{r}
women <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-12-08/women.csv')
```

## Loading libraries
```{r}
library(data.table)
library(plotly)
library(ggplot2)
library(stringr)
library(packcircles)
```


## Which category of a ward had the highest count of influencial women
I'll use data.table library to count the number of women by category and then use the table to visualize the counts.
I'll also calculate the percentages using the counts.
I excluded the first record considering it was left as a tribute and so it doesn't have a category. 
```{r}
category_count <- data.table::data.table(women)[2:100,.(percentage=round(100*.N/nrow(women),0)),by=category]
```

## Bubble chart showing the percentage count of women per category
which category of award had the highest count of influential women in 2020?

### Plotly bubble chart
```{r}
category_count %>%
plot_ly() %>%
      add_trace(x = ~reorder(category, -percentage), 
                y = ~percentage,
                size = ~percentage,
                color = ~category,
                text = ~paste0("Category:  ", category, "\n", "Percentage ", percentage),
                hoverinfo = 'text',
                type = "scatter",
                mode = "markers",
                marker = list(symbol = 'circle', sizemode = 'diameter',
                              line = list(width = 2, color = '#FFFFFF'), opacity=0.6)) %>%
      layout( title = "Category of award comparison",
        showlegend = FALSE,
        xaxis = list(
          title = "Category of award"
        ),
        yaxis = list(
          title = "Percentage count of women"
        )
      ) %>%
      config(displayModeBar = FALSE, displaylogo = FALSE, 
             scrollZoom = FALSE, showAxisDragHandles = TRUE, 
             showSendToCloud = FALSE)
```


### Using ggplot and packcircles libraries
```{r}



    packing.services <- packcircles::circleProgressiveLayout(category_count$percentage, sizetype='area')

    category.packing <- cbind(category_count, packing.services)
    category.data <- packcircles::circleLayoutVertices(packing.services, npoints=50)
    category.packing$id<-1:nrow(category.packing)
    category.data<-dplyr::left_join(category.data,category.packing,by="id")
    category.data<-category.data[,c(1:5)]
    colnames(category.data)[1:2]<-c("x","y")
    
    # Make the plot
  ggplot2::ggplot(data = category.data) +
      geom_polygon(aes(x, y, group = id, fill=str_wrap(category,15), text = paste0("category: ", category)),alpha=.9) +
      geom_text(data = category.packing, aes(x, y), size=5,label =paste0(category_count$category,"\n",category_count$percentage,"%"), fontface="bold") +
      theme_void() +
      theme(legend.position="none",
            plot.title = element_text(size=20,face="bold",hjust=0.5),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            axis.line = element_blank()) +
      coord_equal()+
      ggtitle("Award cagegories of influential women of 2020")+
      scale_fill_brewer(palette = "Set3",name="")+
      guides(fill=guide_legend(nrow=1))

```



## What are the top 10 roles/careers of these influential women?

```{r}
women$role <- gsub("Human-rights activist","Human rights activist",women$role)
career_count <- data.table::data.table(women)[2:100,.(count=.N),by=role][order(-count)][1:15]


career_count %>%
  ggplot(aes(x=count, y = reorder(role,count))) +
  geom_col(fill = "#00688B" ) +
  labs(title = "Top 10 careers of influential women in 2020", x = "Count", y = "Careers") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5))
```

